---
title: "Script Likert plots equity Fiji"
author: ""
date: '2022-04-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#####Load packages

```{r}
#load packages

#library(tidyverse) #there is an error with tidyverse
library(tidyr)
library(ggplot2)
library(dplyr)
library(devtools)
library(stats)
library(ordinal)
library(MASS)
library(ggeffects)
library(effects)
library(scales)
#library(car) #for regression diagnostics
#library(broom) #for tidy output
#library(ggfortify) #for model diagnostics
#library(sjPlot) #for outputs
library(knitr) #for kable
#library(effects) #for partial effects plots
#library(MuMIn) #for interfacing with STAN
#library(emmeans) #for estimating marginal means
#library(ggeffects) #for partial effects plots
#library(MASS) #for glm.nb
#library(MuMIn) #for AICc
#library(DHARMa) #for residual diagnostics plots
#library(modelr) #for auxillary modelling functions
#library(performance) #for residuals diagnostics
#library(see) #for plotting residuals
library(patchwork) #for grids of plots
#library(brms)
#library(bayesplot)
library(coda)
#library(ggmcmc)
#library(broom) #for tidying outputs
library(tidybayes) #for more tidying outputs
#library(broom.mixed)#for summarising models
library(knitr)
library(likert)

```


#Arranging data set

Data 2016, treatment and control communities.

Change name of the data set
#```{r}

data_fiji<-Fiji_data_notabu_2016_4

#```

```{r}

data_fiji<- read.csv ("Fiji_data_notabu_2016.4.csv",
                     header=TRUE,
                    dec=".")

```


Transform variables into factors (District, control/treatment)


```{r}

data_fiji$district<-as.factor(data_fiji$district) #district as factor
levels(data_fiji$district)

data_fiji$village<-as.factor(data_fiji$village) #village as factor
levels(data_fiji$village)

str(data_fiji$PES_exp)
data_fiji$PES_exp<-as.factor(data_fiji$PES_exp) #control and treatment as factor
levels(data_fiji$PES_exp)# two leveles (control and treatment)


dim(data_fiji) # n=193
```

COVARIATES:

AGE

```{r}
#Age (nominal)

str(data_fiji$Age)

ggplot(data_fiji,aes(Age))+geom_bar()

data_fiji$Age_num<-as.numeric(as.character(data_fiji$Age)) 

hist(data_fiji$Age_num) 
```



MIGRANT 

```{r}
#Migrant status (Categorical)

str(data_fiji$Migrant)

#transform in factor
data_fiji$Migrant<-as.factor(data_fiji$Migrant)
str(data_fiji$Migrant)

#Combine Migrant levels 2,3 and 4

data_fiji$Migrant<-as.numeric(as.character( data_fiji$Migrant))
str(data_fiji$Migrant)

data_fiji$migrant2 <- as.factor(ifelse(data_fiji$Migrant > 1,2,1)) 

ggplot(data_fiji,aes(Migrant))+geom_bar()
ggplot(data_fiji,aes(migrant2))+geom_bar()


```

```{r}
#Years living in the village

str(data_fiji$Years_village)

ggplot(data_fiji,aes(Years_village))+geom_bar()


```


```{r}
#Gender

ggplot(data_fiji,aes(Gender))+geom_bar()

str(data_fiji$Gender)

data_fiji$Gender<-as.factor(data_fiji$Gender)


```

```{r}
#Marital status

ggplot(data_fiji,aes(Marital_status))+geom_bar()

str(data_fiji$Marital_status)

data_fiji$Marital_status<-as.factor(data_fiji$Marital_status)


```



```{r}
#Education 

str(data_fiji$Education)

data_fiji$Education<-as.factor(data_fiji$Education)
str(data_fiji$Education)
ggplot(data_fiji,aes(Education))+geom_bar()

data_fiji$Education_num<-as.factor(ifelse(data_fiji$Education == "Primary",1,
                                                   ifelse(data_fiji$Education=="Secondary",2,
                                                          ifelse(data_fiji$Education=="Tertiary",3,0))))


ggplot(data_fiji,aes(Education_num))+geom_bar()

data_fiji$Education_num<-as.numeric(as.character(data_fiji$Education_num))

str(data_fiji$Education_num)

#Transform in Primary, secondary and tertiary

data_fiji$Education<-recode_factor(data_fiji$Education, "Secondary-F5" = "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Secondary-F6" = "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Secondary - F1" = "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Secondary - F4" = "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "primary" = "Primary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "secondary"= "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "tertiary"= "Tertiary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Form 4"= "Tertiary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Form 3"= "Tertiary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Form 5"= "Tertiary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Form 6"= "Tertiary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Form 7"= "Tertiary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Class 2"= "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Class 5"= "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Class 6"= "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Class 7"= "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "class 7"= "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "class 5"= "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "class 8"= "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Class 8"= "Secondary")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "0"= "None")
levels(data_fiji$Education)
data_fiji$Education<-recode_factor(data_fiji$Education, "Intermediate"= "Primary") #assuming intermediate is secondary. CHECKK!!!
levels(data_fiji$Education)
ggplot(data_fiji,aes(Education))+geom_bar()


```



```{r}
data_fiji$Education_cat3<-as.factor(ifelse(data_fiji$Education == "Tertiary",3,
                                                   ifelse(data_fiji$Education=="Secondary",2,1)))
                                                          


```

Wealth

I have calculated wealth using all assets and chose the one with loading factors higher than 0.4 (Gurney and Darling 2017. A Global Social-Ecological Systems Monitoring Framework for Coastal Fisheries Management: A Practical Monitoring Handbook)


calculate wealth (Material lifestyle)



```{r}
#dvd
str(data_fiji$dvd)
data_fiji$dvd<-as.factor(data_fiji$dvd)
ggplot(data_fiji,aes(dvd))+geom_bar()
which(is.na(data_fiji$dvd))


#washing
str(data_fiji$washing)
data_fiji$washing<-as.factor(data_fiji$washing)
ggplot(data_fiji,aes(washing))+geom_bar()
which(is.na(data_fiji$washing))
#computer
str(data_fiji$computer)
data_fiji$computer<-as.factor(data_fiji$computer)
ggplot(data_fiji,aes(computer))+geom_bar()
which(is.na(data_fiji$computer))
#fridge
str(data_fiji$fridge)
data_fiji$fridge<-as.factor(data_fiji$fridge)
ggplot(data_fiji,aes(fridge))+geom_bar()
which(is.na(data_fiji$fridge))
#tv
str(data_fiji$tv)
data_fiji$tv<-as.factor(data_fiji$tv)
ggplot(data_fiji,aes(tv))+geom_bar()
which(is.na(data_fiji$tv))
#satellite
str(data_fiji$satellite)
data_fiji$satellite<-as.factor(data_fiji$satellite)
ggplot(data_fiji,aes(satellite))+geom_bar()
data_fiji<-data_fiji%>% 
  mutate(satellite=na_if(satellite, "no answer"))
which(is.na(data_fiji$satellite))#187 is missing


#recode rest of the variables

data_fiji$dvd<-recode_factor(data_fiji$dvd,"y" ="1")
data_fiji$dvd<-recode_factor(data_fiji$dvd,"n" ="0")

data_fiji$smartphone<-recode_factor(data_fiji$smartphone,"y" ="1")
data_fiji$smartphone<-recode_factor(data_fiji$smartphone,"n" ="0")

data_fiji$washing<-recode_factor(data_fiji$washing,"y" ="1")
data_fiji$washing<-recode_factor(data_fiji$washing,"n" ="0")

data_fiji$fridge<-recode_factor(data_fiji$fridge,"y" ="1")
data_fiji$fridge<-recode_factor(data_fiji$fridge,"n" ="0")

data_fiji$tv<-recode_factor(data_fiji$tv,"y" ="1")
data_fiji$tv<-recode_factor(data_fiji$tv,"n" ="0")

data_fiji$satellite<-recode_factor(data_fiji$satellite,"y" ="1")
data_fiji$satellite<-recode_factor(data_fiji$satellite,"n" ="0")

#transform variable into numeric vars
data_fiji$dvd<-as.numeric(as.character(data_fiji$dvd))
which(is.na(data_fiji$dvd))
data_fiji$washing<-as.numeric(as.character(data_fiji$washing))
which(is.na(data_fiji$washing))
data_fiji$fridge<-as.numeric(as.character(data_fiji$fridge))
which(is.na(data_fiji$fridge))
data_fiji$tv<-as.numeric(as.character(data_fiji$tv))
which(is.na(data_fiji$tv))
data_fiji$satellite<-as.numeric(as.character(data_fiji$satellite))
which(is.na(data_fiji$satellite)) #missing 187


#PCA 18 only have one missing value.

data_fiji<-data_fiji[-c(187),]
wealth_rows_pca18.2= data_fiji[, c("dvd", "washing","fridge","tv", "satellite")]
xord18.2<-prcomp(wealth_rows_pca18.2, center= TRUE, scale=TRUE)

summary(xord18.2)

biplot(xord18.2)


loadings18.2<-xord18.2$rotation #rotation is the matrix of variable loadings (columns are eigenvectors) in prcomp() function
loadings18.2 



#extract pc1


myscores.2<-xord18.2$x # "x" are the coordinates of the individuals (observations) on the principal components in prcomp()

data_fiji$wealth_msl.2<-myscores.2[,"PC1"] #add this to fiji_data and add na to the empty cells

data_fiji$wealth_msl.2



str(data_fiji$wealth_msl.2)

data_fiji$wealth_msl.2_sc.1<-scale( data_fiji$wealth_msl.2, center = TRUE,scale=TRUE)


data_fiji$wealth_msl.2.resc<- rescale(data_fiji$wealth_msl.2, to = c(0,1)) #rescale

hist(data_fiji$wealth_msl.2)


```


```{r}
hist(data_fiji$wealth_msl.2.resc)
```


```{r}
data_fiji$wealth2<-data_fiji$wealth_msl.2.resc
```


```{r}
#gender (Gender) 
str(data_fiji$Gender)
#marital status
str(data_fiji$Marital_status)
#age (Age)
str(data_fiji$Age_num)
hist(data_fiji$Age_num)
#migrant status (migrant2)
str(data_fiji$migrant2)
#years in the village
str(data_fiji$Years_village)
#education (Education)
str(data_fiji$Education)
str(data_fiji$Education_cat3)
#wealth
str(data_fiji$wealth_msl.2)
str(data_fiji$wealth2)

```


Standardize


```{r}

# Scale all "numerical" variables from 0 to 1
#migrant: binomial

#data_fiji$n_children_sd <- scale(data_fiji$n_children)*0.5
data_fiji$wealth2_sd <- scale(data_fiji$wealth2)*0.5
data_fiji$Years_village_sd<-scale(data_fiji$Years_village)*0.5
data_fiji$Age_num_sd <- scale(data_fiji$Age_num)*0.5

```

Save data with previous steps
```{r}
#write.csv(data_fiji,'data_fiji2.2.csv')
```



RESPONSE VARIABLES

I am going to create a data set for procedural equity and another one for distributional equity to avoid the elimnations of nas in procedural equity resulting from nas occuring only in disributional equity and viceversa.

DISTRIBUTIONAL EQUITY

```{r}
ggplot(data_fiji, aes(Distr_Eq_Impact))+geom_bar()
```



Eliminate NA and don't knows (including 6), and noanswer
```{r}
data_fiji_dist <- data_fiji[data_fiji$Distr_Eq_Impact!=6,]

data_fiji_dist <- data_fiji_dist[data_fiji_dist$Distr_Eq_Impact!=7,]

data_fiji_dist <- data_fiji_dist[data_fiji_dist$Distr_Eq_Impact!="dontknow",]

data_fiji_dist<- data_fiji_dist[data_fiji_dist$Distr_Eq_Impact!="noanswer",]

which(is.na(data_fiji_dist$Distr_Eq_Impact))

data_fiji_dist <- data_fiji_dist[data_fiji_dist$Distr_Eq_Impact!="na",]

```
```{r}
ggplot(data_fiji_dist, aes(Distr_Eq_Impact))+geom_bar()
```

```{r}
ggplot(data_fiji_dist, aes(Distr_Eq_Impact,fill=Gender))+geom_bar()+theme_classic()
  

```

```{r}
dim(data_fiji_dist)
```

```{r}
which(is.na(data_fiji_dist$Age_num_sd))
```

There in 1 NA in age withing data_fiji_dist.

```{r}
data_fiji_dist<-data_fiji_dist[-c(43),]
```


```{r}
str(data_fiji_dist$Distr_Eq_Impact)
```

```{r}
data_fiji_dist$Distr_Eq_Impact_int<-as.integer(data_fiji_dist$Distr_Eq_Impact)
```

```{r}
str(data_fiji_dist$Distr_Eq_Impact_int)
```



Likert plot

```{r}
data_fiji_dist$Distr_Eq_Impact_cat<-as.factor(ifelse(data_fiji_dist$Distr_Eq_Impact==1,"Very unfair",
                               ifelse(data_fiji_dist$Distr_Eq_Impact==2, "Unfair",
                                      ifelse(data_fiji_dist$Distr_Eq_Impact==3, "Neutral",
                                             ifelse(data_fiji_dist$Distr_Eq_Impact==4, "Fair","Very fair")))))
                                      
```

```{r}
gender_summary<-data_fiji_dist%>%
  group_by(Gender)%>%
  count(name="n_answers")
```

```{r}
gender_summary
```

```{r}
edu_summary<-data_fiji_dist%>%
  group_by(Education_cat3)%>%
  count(name="n_answers")
```

```{r}
mar_summary<-data_fiji_dist%>%
  group_by(Marital_status)%>%
  count(name="n_answers")
```

```{r}
genmig_summary<-data_fiji_dist%>%
  group_by(Gender,migrant2)%>%
  count(name="n_answers")
```

```{r}
genmar_summary<-data_fiji_dist%>%
  group_by(Gender,Marital_status)%>%
  count(name="n_answers")
```

```{r}
genedu_summary<-data_fiji_dist%>%
  group_by(Gender,Education_cat3)%>%
  count(name="n_answers")
```

```{r}

de_summary<-data_fiji_dist%>%
  group_by(Gender, Distr_Eq_Impact_cat)%>%
  count(name="n_answers")%>%
  group_by(Gender)
#%>%
  #mutate(percent_answers=n_answers/sum(n_answers))%>%
  #ungroup()%>%
#mutate(percent_answers_label = percent(percent_answers,accuracy=1))
  

```
wide format

```{r}
de_summary
```


    ```{r}
de_gender_wide<-de_summary%>% 
    pivot_wider(names_from = Distr_Eq_Impact_cat, values_from =n_answers)
    
```


    ```{r}
de_gender_wide
    
```

    ```{r}
col_order<-c("Gender","Very unfair", "Unfair", "Neutral", "Fair", "Very fair")
    
```

    ```{r}
de_gender_wide_or<-de_gender_wide[,col_order]
    
```


    ```{r}
de_gender_wide_or
    
```


```{r}

HH::likert(Gender~.,data=de_gender_wide_or, ylab=NULL, ReferenceZero=3,as.percent=TRUE,
           main = list("Distributional Equity"))
         
           
```

```{r}

plot_de<-HH::likert(Gender~.,data=de_gender_wide_or, ylab=NULL, ReferenceZero=3,as.percent=TRUE,
           main = list("Distributional Equity"))
         
           
```

```{r}
Gender<-c("Women", "Men")
Very_unfair<-c(3,3)
Unfair<-c(13,11)
Neutral<-c(10,3)
Fair<-c(35,40)
Very_fair<-c(16,23)

df_dist_eq<-data.frame(Gender, Very_unfair, Unfair, Neutral, Fair, Very_fair)
print(df_dist_eq)

```

```{r}

HH::likert(Gender~.,data=df_dist_eq, ylab=NULL, ReferenceZero=3, as.percent=TRUE,
           main = list("Distributional Equity"))
         
           
```




PROCEDURAL EQUITY

```{r}
ggplot(data_fiji, aes(Proced_Equity))+geom_bar()
```



Eliminate NA and don't knows (including 6), and noanswer
```{r}
data_fiji_proced <- data_fiji[data_fiji$Proced_Equity!=6,]

data_fiji_proced <- data_fiji_proced[data_fiji_proced$Proced_Equity!="dontknow",]

data_fiji_proced<- data_fiji_proced[data_fiji_proced$Proced_Equity!="noanswer",]

which(is.na(data_fiji_proced$Proced_Equity))

data_fiji_proced<- data_fiji_proced[data_fiji_proced$Proced_Equity!="na",]

```




```{r}
ggplot(data_fiji_proced, aes(Proced_Equity))+geom_bar()
```



```{r}
dim(data_fiji_proced)
```



```{r}
str(data_fiji_proced$Proced_Equity)
```
```{r}
data_fiji_proced$Proced_Equity_int<-as.integer(data_fiji_proced$Proced_Equity)
```


```{r}
str(data_fiji_proced$Proced_Equity_int)
```


Likert plot




```{r}
data_fiji_proced$Proced_Equity_cat<-as.factor(ifelse(data_fiji_proced$Proced_Equity_int==1,"Very unfair",
                               ifelse(data_fiji_proced$Proced_Equity_int==2, "Unfair",
                                      ifelse(data_fiji_proced$Proced_Equity_int==3, "Neutral",
                                             ifelse(data_fiji_proced$Proced_Equity_int==4, "Fair","Very fair")))))
                                      
```

```{r}

pe_summary<-data_fiji_proced%>%
  group_by(Gender, Proced_Equity_cat)%>%
  count(name="n_answers")%>%
  group_by(Gender)
#%>%
  #mutate(percent_answers=n_answers/sum(n_answers))%>%
  #ungroup()%>%
#mutate(percent_answers_label = percent(percent_answers,accuracy=1))
  

```

```{r}

pe_summary
  

```

```{r}
gen_summary<-data_fiji_proced%>%
   group_by(Gender)%>%
   count(name="n_answers")

```

```{r}
mig_summary<-data_fiji_proced%>%
   group_by(migrant2)%>%
   count(name="n_answers")

```

```{r}
mar_summary<-data_fiji_proced%>%
   group_by(Marital_status)%>%
   count(name="n_answers")

```

```{r}
edu_summary<-data_fiji_proced%>%
   group_by(Education_cat3)%>%
   count(name="n_answers")

```

```{r}
genmig_summary<-data_fiji_proced%>%
   group_by(Gender,migrant2)%>%
   count(name="n_answers")

```

```{r}
genmar_summary<-data_fiji_proced%>%
   group_by(Gender,Marital_status)%>%
   count(name="n_answers")

```

```{r}
gened_summary<-data_fiji_proced%>%
   group_by(Gender,Education_cat3)%>%
   count(name="n_answers")

```

    ```{r}
pe_gender_wide<-pe_summary%>% 
    pivot_wider(names_from = Proced_Equity_cat, values_from =n_answers)
    
```


    ```{r}
pe_gender_wide
    
```


    ```{r}
pe_gender_wide_or<-pe_gender_wide[,col_order]
    
```

```{r}

HH::likert(Gender~.,data=pe_gender_wide_or, ylab=NULL, ReferenceZero=3, as.percent=TRUE,main = list("Procedural Equity"))
         
           
```



```{r}

plot_pe<-HH::likert(Gender~.,data=pe_gender_wide_or, ylab=NULL, ReferenceZero=3, as.percent=TRUE,main = list("Procedural Equity"))
         
           
```




```{r}
 library(ggpubr)          
```



```{r}
    ggarrange(plot_de,plot_pe, ncol = 1, nrow = 2,
          labels = c("A", "B"))
```

